### 2017-01-07 README.Rmd
Clean up typos in README.Rmd.

There are two main commands in the `visdat` package: 
- `vis_dat()` 
- `vis_miss()`

@@

There are two some experimental functions:

- `vis_guess()`
- `vis_compare()`

@@

by default, `vis_dat` sorts the columns according to the type of the data in the vectors. You can turn this off by setting `sort_type == FALSE`. This feature is better illustrated using the `airquality` dataset from base R.

@@

The plot above tells us that R reads this dataset as having characters, and integer values, along with some missing data in `Ozone` and `Solar.R`.

### with different data

To demonstrate what visdat looks like when you have different kinds of data, we can look at the `typical_data` from within visdat, created using the excellent [`wakefield package`](https://github.com/trinker/wakefield).

@@

## using `vis_miss()`

@@

## using `vis_compare()`

@@

Here the differences are marked in red.

@@

## using `vis_guess()`

@@

Where you'd just assume your data is wierd because it's all factors - or worse, not notice that this is a problem.

@@

**visualising expectations**

@@

Thank you to Ivan Hanigan who [first commented](http://www.njtierney.com/r/missing%20data/rbloggers/2015/12/01/ggplot-missing-data/#comment-2388263747) this suggestion after I made a blog post about an initial prototype `ggplot_missing`, and Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions that removed a lot of errors.

@@

Thank you to Miles McBain for his suggestions on how to improve vis guess. This resulted in making it at least 2-3 times faster.

Thanks also to Carson Sievert for writing the code that combined plotly with visdat, and for Noam Ross for suggesting this in the first place.

>>>>

There are two main commands in the `visdat` package:

@@

There are two experimental functions:

@@

by default, `vis_dat` sorts the columns according to the type of the data in the vectors. You can turn this off by setting `sort_type = FALSE`. This feature is better illustrated using the `airquality` dataset from base R.

@@

The plot above tells us that R reads this dataset as having characters and integer values, along with some missing data in `Ozone` and `Solar.R`.

### With many kinds of data

To demonstrate what visdat looks like when you have different kinds of data, we can use `visdat` to look at the dataset `typical_data`, which is from the excellent [`wakefield package`](https://github.com/trinker/wakefield).

@@

## Using `vis_miss()`

@@

## Using `vis_compare()`

@@

Here the differences are marked in blue.

@@

## Using `vis_guess()`

@@

Where you'd just assume your data is weird because it's all factors - or worse, not notice that this is a problem.

@@

**Visualising expectations**

@@

Thank you to Ivan Hanigan who [first commented](http://www.njtierney.com/r/missing%20data/rbloggers/2015/12/01/ggplot-missing-data/#comment-2388263747) this suggestion after I made a blog post about an initial prototype `ggplot_missing`, and Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about `vis_dat`, and for her code contributions that removed a lot of errors.

@@

Thank you to Miles McBain for his suggestions on how to improve `vis_guess`. This resulted in making it at least 2-3 times faster.

Thanks also to Carson Sievert for writing the code that combined `plotly` with `visdat`, and for Noam Ross for suggesting this in the first place.
